%-------------------------
% Resume in Latex
% Author: Panambur Pawan Bhandarkar 
% License: MIT
%------------------------

\documentclass[letterpaper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries{}
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingWithoutTitle}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\textit{#1}} & \textit{\small #2} \\
    \end{tabular*}\vspace{-14pt}
}
\newcommand{\resumeSubheading}[4]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textbf{\textit{#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}



\newcommand{\shortSection}[1]{
    \vspace{-6pt}
    \section{#1}
}

\newcommand{\educationHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & {#2} \\
        \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}
    \small{\textbf{Courses :}{#5}}
}

\newcommand{\projectHeading}[3]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} 
        \hspace{-2pt} $\vert$ \hspace{-2pt} \small{\textit{#2}} 
        & 
        \textit{#3} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand*{\skill}[2]{
  \textbf{#1 : }#2 \\
  \vspace{1pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{{\LARGE Panambur Pawan Bhandarkar}}\\
  Mountain View, CA & Portfolio:\href{https://www.bhandarkar.me/}{ \color{blue}{https://bhandarkar.me}} \\
  Email : \href{mailto:panambub@andrew.cmu.edu}{panambub@andrew.cmu.edu}   &   Github:\href{https://github.com/BhandarkarPawan}{ \color{blue}{https://github.com/BhandarkarPawan}}\\
  Mobile : +1-650-537-7341 &  Linkedin:\href{https://www.linkedin.com/in/bhandarkar/}{ \color{blue}{https://www.linkedin.com/in/bhandarkar}} \\

\end{tabular*}


%-----------SUMMARY-----------------
% \shortSection {Summary}
% \small Full-stack engineer experienced (2+ years) in building \textbf{responsive}, \textbf{accessible} web applications. I write \textbf{clean, modular}, \textbf{well-documented} and testable code that is easy for teams to \textbf{understand, extend}, and \textbf{integrate}. 



%-----------EDUCATION-----------------
\shortSection{Education}
\educationHeading
{Carnegie Mellon University}{Mountain View, CA}
{Master of Science in Software Engineering; \textbf{GPA: 4.0/4.0} }{Aug 2022 - Dec 2023}{
  Foundations of Software Engineering,
  Software Verification \& Testing,
  HCI \& UX,
  Data Science for Software Engineering
}

\vspace{5pt}

\educationHeading
{NMAM Institute of Technology }{Nitte, India}
{Bachelor of Computer Science;  \textbf{GPA: 9.8/10} (top 1\%, Class of 2020) }{Jul 2016 - Apr 2020}{
  Data Structures \& Algorithms,
  Object Oriented Modelling \& Design,
  Linear Algebra \& Probability Theory
}


%-------- SKILLS------------
\shortSection{Skills}
\skill {Languages}{Typescript, JavaScript (ES6+), Python, SQL, NoSQL, HTML5, CSS, XML, JSON, GraphQL,  Java,  C++}
\skill {Libraries \& Frameworks}{React, NodeJS, Flask, PostgreSQL, Express, Bootstrap, Redux, Styled-Components, MongoDB, Sass}
\skill {Tools}{Figma, Docker, AWS, S3, Postman, VSCode, Git, Miro, Jama}


%-----------EXPERIENCE-----------------
\shortSection{Experience}
\resumeSubheading
{Team AIBOD Inc.}{Fukuoka City, Japan}
{Software Engineer 2}{Nov 2021 - Apr 2022}
\vspace{2pt}
\resumeItemListStart
\resumeItemWithoutTitle{Developed a comprehensive component library with \textbf{React and Typescript} for an unmanned store, enhancing accessibility through touch-screen and voice-based interface, accelerating UI development and streamlining the overall development process}
\resumeItemWithoutTitle{Implemented a \textbf{RESTful} payment server using \textbf{Python, Flask}, and \textbf{PostgreSQL for CRUD operations}, resulting in the expansion of customer base by including BioPay users, contributing to $\sim$¥500K increase in annual revenue.}
\resumeItemWithoutTitle{Containerized and deployed applications using \textbf{Docker}, and set up \textbf{AWS Cloudwatch} for remote monitoring of unmanned stores across 5 customer locations, ensuring smooth and efficient operations.}
\resumeItemWithoutTitle{\textbf{Mentored 3 interns} from IIT Hyderabad, promoting technical and professional growth in a collaborative environment.}
\resumeItemListEnd

\vspace{2pt}
\resumeSubheadingWithoutTitle
{Software Engineer 1}{Jul 2020 - Oct 2021}
\vspace{0pt}
\resumeItemListStart
\resumeItemWithoutTitle{Created a \textbf{Python script} and a GUI-tool using \textbf{Tkinter} for annotating and visualizing images, increasing the data pre-processing rate from 20 to 200 images/hour and improving team productivity.}
\resumeItemWithoutTitle{Designed and implemented a Search System using \textbf{GraphQL} with \textbf{Apollo} and \textbf{Ariadne}, streamlining 3 ongoing projects.}
% \resumeItemWithoutTitle{Improved team efficiency and reliability with over 80\% code coverage through unit and integration \textbf{testing} with \textbf{Jest.}}
\resumeItemWithoutTitle{Introduced \textbf{unit and integration tests} with \textbf{Jest} which improved team efficiency and reliability with over 80\% coverage.}
\resumeItemListEnd

\vspace{2pt}
\resumeSubheadingWithoutTitle
{AI Engineer Intern}{Feb 2020 - Jun 2020}
\vspace{0pt}
\resumeItemListStart
\resumeItemWithoutTitle{Applied \textbf{Feature Engineering} to improve the accuracy of a \textbf{KNN-supervised classifier} by 7\%, resulting in more effective classification of products in an unmanned store.}
\resumeItemWithoutTitle{Experimented with \textbf{BERT} using \textbf{PyTorch} for \textbf{Named Entity Recognition} to automate support request routing in an apartment intercom system and integrated it with the \textbf{Express API Server} to provide AI as a Service.}
\resumeItemWithoutTitle{Expertly resolved more than 20 bugs in the API server using \textbf{NodeJS and Typescript}, resulting in improved stability and performance of the server, also contributed to ongoing full-stack applications.}
\resumeItemListEnd

%-----------PROJECTS-----------------



\shortSection{Projects}
\vspace{3pt}
\projectHeading {\href{https://esn.onrender.com}{\color{blue}{Emergency Social Network}}}{HTML, CSS, TypeScript, NodeJS, MongoDB}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Built a web-based emergency communication system for real-time SOS messaging during earthquakes. Utilized \textbf{SCRUM} and \textbf{Kanban} agile practices, \textbf{OOAD}, and a test-driven development approach to create a highly maintainable and user-friendly system with \textbf{JSON-based RESTful APIs.}}
\resumeItemListEnd


\projectHeading {\href{https://kanbhan.netlify.app}{\color{blue}{Kanban Task Manager}}}{React, NodeJS, Styled-Components, Figma}{Jun 2022 - Present}
\resumeItemListStart
\resumeItemWithoutTitle{Developed a highly accessible Kanban Task Manager using \textbf{Client-Server} architecture with \textbf{React Hooks} and \textbf{Context API} focussing on \textbf{A11y, Semantic HTML, and ARIA labels}, which ensured usability with screen readers such as Apple Voice-Over. Generated clear API documentation with \textbf{API Blueprint} and \textbf{Postman.}}
\resumeItemListEnd


\vspace{3pt}
\projectHeading {\href{https://mailchi.mp/6cf20f3d592f/reuse}{\color{blue}{Re:use}}}{React, Typescript, NodeJS, MongoDB, Figma, Jama, Miro}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Led the development of the \textbf{MVP} for a Resource Management application in the donation industry by generating style guides in \textbf{Figma}, and converting user requirements into working software using the \textbf{MERN} Stack.}
% \resumeItemWithoutTitle{\textbf{Ideated} a solution for problems faced by the donation industry through \textbf{usability studies} and \textbf{contextual inquiries} with Stakeholders. Generated \textbf{affinity diagrams}, \textbf{personas}, and \textbf{story boards} to envision a solution using the Dual-Track Agile process. Worked as an interaction designer to drive user research/interviews, create a core product vision and build a MVP.}
\resumeItemListEnd

\vspace{3pt}
\projectHeading {\href{https://www.figma.com/file/FpWVddCZKdJz5V7ADe4eb5/Refriendo}{\color{blue}{Refriendo}}}{TypeScript, React, CSS, Figma, Git}{Oct 2021 - Jul 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Implemented a cross-platform Event Management Application for both \textbf{Android} and \textbf{iOS} using \textbf{React} and \textbf{Ionic Capacitor}. Designed and iteratively improved the user interface through high-fidelity \textbf{Figma} prototypes and think-aloud usability testing surveys, resulting in a clean, visually appealing design aesthetic.}
\resumeItemListEnd

%-------- AWARDS------------
\shortSection{Awards \& Leadership}
\skill{Graduate Teaching Assistant}{Foundations of Software Engineering at Carnegie Mellon University.}
\skill{Student Leader}{ECE Graduate Organization at Carnegie Mellon University (Among 160 students).}
\skill{Youth Icon (title)}{Won first place in a national public speaking competition among 5000 participants in March 2019.}

\end{document}


